Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-01 paper/paper.qmd
Modify reference

## Core Objectives
* Obtain a representative sample of the U.S. electorate, with demographic diversity mirroring national voting patterns.
* Ensure data quality through rigorous validation processes, including screening and cross-verification.
* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling [@silver_nytimes].

@@

These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @silver_nytimes].

## Poll Aggregation and Data Analysis
### Poll Aggregation
This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@silver_nytimes].

>>>>

## Core Objectives
* Obtain a representative sample of the U.S. electorate, with demographic diversity mirroring national voting patterns.
* Ensure data quality through rigorous validation processes, including screening and cross-verification.
* Utilize statistical modeling and poll aggregation techniques to provide accurate predictions, as outlined in prior studies of electoral polling

@@

These practices align with standards for data integrity and quality control in electoral polling [@fivethirty; @pew_survey_methodology].

## Poll Aggregation and Data Analysis
### Poll Aggregation
This survey will be combined with results from reputable polling firms (e.g., YouGov, Ipsos, Gallup) to strengthen the forecast through a **poll-of-polls** approach [@pew_survey_methodology].
